Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
no crossdressing Kumyks
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60990 72bbbca6-d526-0410-a7d9-f06f51895060

Future work will focus on improving the annotation guidelines and the consistency of
annotation in the corpus. We will also study the possibility of deepening the annotation
with Turkic-specific relations. When we have stable annotation guidelines we intend to 
extend the corpus with more texts.
We would also like to work on cross-lingual dependency parsing,
that is, applying a model learnt on the Kazakh treebank to other Turkic languages
such as Tatar, Kumyk and Tuvan. We have morphological analysers for these languages which have
compatible tagsets for morphological features and as such it should be possible to learn a
delexicalised model based on these features. As Turkic syntax is broadly homogenous, this
presents a promising avenue for future work.

>>>>

Future work will focus on improving the annotation guidelines and the consistency of
annotation in the corpus. We will also study the possibility of deepening the annotation
with Turkic-specific relations. When we have stable annotation guidelines we intend to 
extend the corpus with more texts.
We would also like to work on cross-lingual dependency parsing,
that is, applying a model learnt on the Kazakh treebank to other Turkic languages
such as Tatar, Kumyk, and Tuvan. We have morphological analysers for these languages which have
compatible tagsets for morphological features and as such it should be possible to learn a
delexicalised model based on these features. As Turkic syntax is broadly homogenous, this
presents a promising avenue for future work.
